Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
fixed Appendix B

\section{Integral Equation Formulation}
\label{sec:AppendixB}
Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
%
\begin{align*}
  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
  &\xx_s \cdot \dot{\xx}_s = 0,
 \end{align*}
%
where the single-layer potential $\SS[\cdot]$ is defined by
\begin{align}
  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
    \xxi(\yy) ds_\yy, 
  \label{eqn:SLP}
\end{align}
%
and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
\begin{equation*}
\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
\end{equation*}
Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and
using IMEX-Euler, the no-slip boundary results in the time stepping
method
\begin{align*}
  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
    \Delta t \SS^N \AA^N \xx^N,
\end{align*}
and the inextensibility constraint that is discretized as
\begin{align*}
  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
\end{align*}
We discretize the vesicles at a set of collocation points, compute the
bending and tension terms with Fourier differentiation, and apply Alpert
quadrature~\cite{alp1999} to the weakly-singular single-layer potential
$\SS$.  The source and target points of the adhesion force never
coincide since they are always on different vesicles, so the adhesion
force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
trapezoid rule~\cite{tre-wei2014}.

@@

To characterize the rheological properties of the suspension of a
doublet, it is necessary to compute the shear and normal stresses.  At a
point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
are
\begin{align*}
  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
    \ff ds_\yy, \\
    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
      \frac{\rr \cdot \ff}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
\end{align*}
where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
stress tensor on a vesicle, there is a jump in the layer potential
$\SS_T$, and the stress tensor is
\begin{align*}
  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \ff \right) + 
  \SS_T[\ff](\xx), \quad \xx \in \gamma,
\end{align*}
where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
vector, respectively.  With the stress tensor computed for $\xx \in
\gamma$, the shear and normal stresses are
\begin{align*}
  \tau^\tt = (T \nn) \cdot \tt, \qquad
  \tau^\nn = (T \nn) \cdot \nn.
\end{align*}

>>>>

\section{Integral Equation Formulation}
\label{sec:AppendixB}
Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
%
\begin{align*}
  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
  &\xx_s \cdot \dot{\xx}_s = 0,
 \end{align*}
%
where the single-layer potential $\SS[\cdot]$ is defined by
\begin{align}
  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
    \xxi(\yy) ds_\yy, 
  \label{eqn:SLP}
\end{align}
%
and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
\begin{align*}
\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
\end{align*}
Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and using
IMEX-Euler, the no-slip boundary results in the time stepping method
\begin{align*}
  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
    \Delta t \SS^N \AA^N \xx^N,
\end{align*}
and the inextensibility constraint that is discretized as
\begin{align*}
  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
\end{align*}
We discretize the vesicles at a set of collocation points, compute the
bending and tension terms with Fourier differentiation, and apply Alpert
quadrature~\cite{alp1999} to the weakly-singular single-layer potential
$\SS$.  The source and target points of the adhesion force never
coincide since they are always on different vesicles, so the adhesion
force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
trapezoid rule~\cite{tre-wei2014}.

@@

To characterize the rheological properties of the suspension of a
doublet, it is necessary to compute the shear and normal stresses.  At a
point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
of the single-layer potential~\eqref{eqn:SLP} are
\begin{align*}
    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
\end{align*}
To compute the stress tensor on a vesicle, there is a jump in the layer
potential, and the stress tensor is
\begin{align*}
  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \xxi \right) + 
  \SS_T[\xxi](\xx), \quad \xx \in \gamma,
\end{align*}
where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
vector, respectively.  With the stress tensor computed for $\xx \in
\gamma$, the shear and normal stresses are
\begin{align*}
  \tau^\tt = (T \nn) \cdot \tt, \qquad
  \tau^\nn = (T \nn) \cdot \nn.
\end{align*}
